<!--
|  (C) 2006-2024 Potsdam Institute for Climate Impact Research (PIK)
|  authors, and contributors see CITATION.cff file. This file is part
|  of REMIND and licensed under AGPL-3.0-or-later. Under Section 7 of
|  AGPL-3.0, you are granted additional permissions described in the
|  REMIND License Exception, version 1.0 (see LICENSE file).
|  Contact: remind@pik-potsdam.de
-->
# Air Pollutants for CMIP7 harmonization - REMIND

```{r, echo = FALSE, results = 'hide'}
# Adds a new variable as the sum of a list of variables
addSumVariables <- function(
  fdata, sumvars, outvarname, outunit = NULL, convmult = 1, convoffset = 0, only.new = FALSE
  ) {
  if (is.null(outunit)) {
    outunit <- fdata %>%
      filter(variable == sumvars[1]) %>%
      slice(1) %>%
      select(unit) %>% unlist %>% as.character
  }

  newdata <- fdata %>%
    filter(variable %in% sumvars) %>%
    select(-varplus) %>%
    distinct %>%
    pivot_wider(names_from = variable, values_from = value) %>%
    mutate(value = rowSums(across(sumvars))) %>%
    select(-c(sumvars)) %>%
    mutate(variable = outvarname, varplus = outvarname, unit = outunit)
  if(!only.new) {
    return(rbind(fdata, newdata))
  } else {
    return(newdata)
  }
}
```

```{r, echo = FALSE, results = 'hide'}

# Compute total emissions for CMIP7 harmonization sectors from REMIND
for (species in c("BC", "CO", "NH3", "NOx", "OC", "SO2", "VOC")) {
  sumvars <- c(
    paste0("Emi|", species, "|w/ Bunkers|Energy and Industrial Processes"),
    paste0("Emi|", species, "|Product Use|Solvents"),
    paste0("Emi|", species, "|Waste")
  )
  
  data <- data %>% 
    filter(model == "REMIND") %>%
    addSumVariables(sumvars, paste0("Emi|", species,"|REMIND total"), only.new = TRUE) %>%
    bind_rows(data)
}

# Compute emissions for CMIP7 industrial sector from REMIND
for (species in c("BC", "CO", "NH3", "NOx", "OC", "SO2", "VOC")) {
  sumvars <- c(
    paste0("Emi|", species, "|Energy|Demand|Industry"),
    paste0("Emi|", species, "|Industrial Processes")
  )
  
  data <- data %>% 
    filter(model == "REMIND") %>%
    addSumVariables(sumvars, paste0("Emi|", species,"|Industrial Sector"), only.new = TRUE) %>%
    bind_rows(data)
}

# Compute total emissions for CMIP7 harmonization sectors from CEDS
for (species in c("BC", "CO", "NH3", "NOX", "OC", "Sulfur", "VOC")) {
  sumvars <- c(
    paste0("Emi|", species, "|Aircraft"),
    paste0("Emi|", species, "|International Shipping"),
    paste0("Emi|", species, "|Energy Sector"),
    paste0("Emi|", species, "|Industrial Sector"),
    paste0("Emi|", species, "|Residential Commercial Other"),
    paste0("Emi|", species, "|Solvents Production and Application"),
    paste0("Emi|", species, "|Transportation Sector"),
    paste0("Emi|", species, "|Waste")
  )
  
  data <- data %>% 
    filter(model == "CEDS IAMC sectors") %>%
    addSumVariables(sumvars, paste0("Emi|", species,"|REMIND total"), only.new = TRUE) %>%
    bind_rows(data)
}
```

## BC

### Emi|BC|REMIND total
```{r BC Emissions - REMIND Total}
showLinePlots(data, "Emi|BC|REMIND total", histVars = "Emi|BC|REMIND total", vlines = 2020)
```

### Emi|BC|Extra|Energy|Demand|Transport|Pass|Aviation
```{r BC Emissions - Aviation}
showLinePlots(data, "Emi|BC|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|BC|Aircraft", vlines = 2020)
```

### Emi|BC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r BC Emissions - International Shipping}
showLinePlots(data, "Emi|BC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|BC|International Shipping", vlines = 2020)
```

### Emi|BC|Energy|Supply
```{r BC Emissions - Energy Supply}
showLinePlots(data, "Emi|BC|Energy|Supply", histVars = "Emi|BC|Energy Sector", vlines = 2020)
```

### Emi|BC|Energy|Demand|Industry
```{r BC Emissions - Industry}
showLinePlots(data, "Emi|BC|Industrial Sector", histVars = "Emi|BC|Industrial Sector", vlines = 2020)
```

### Emi|BC|Energy|Demand|Buildings
```{r BC Emissions - Buildings}
showLinePlots(data, "Emi|BC|Energy|Demand|Buildings", histVars = "Emi|BC|Residential Commercial Other", vlines = 2020)
```

### Emi|BC|Product Use|Solvents
```{r BC Emissions - Solvents}
showLinePlots(data, "Emi|BC|Product Use|Solvents", histVars = "Emi|BC|Product Use|Solvents Production and Application", vlines = 2020)
```

### Emi|BC|w/o Bunkers|Energy|Demand|Transport
```{r BC Emissions - Transport}
showLinePlots(data, "Emi|BC|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|BC|Transportation Sector", vlines = 2020)
```

### Emi|BC|Waste
```{r BC Emissions - Waste}
showLinePlots(data, "Emi|BC|Waste", histVars = "Emi|BC|Waste", vlines = 2020)
```


## CO

### Emi|CO|REMIND total
```{r CO Emissions - REMIND Total}
showLinePlots(data, "Emi|CO|REMIND total", histVars = "Emi|CO|REMIND total", vlines = 2020)
```

### Emi|CO|Extra|Energy|Demand|Transport|Pass|Aviation
```{r CO Emissions - Aviation}
showLinePlots(data, "Emi|CO|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|CO|Aircraft", vlines = 2020)
```

### Emi|CO|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r CO Emissions - International Shipping}
showLinePlots(data, "Emi|CO|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|CO|International Shipping", vlines = 2020)
```

### Emi|CO|Energy|Supply
```{r CO Emissions - Energy Supply}
showLinePlots(data, "Emi|CO|Energy|Supply", histVars = "Emi|CO|Energy Sector", vlines = 2020)
```

### Emi|CO|Industrial Sector
```{r CO Emissions - Industry}
showLinePlots(data, "Emi|CO|Industrial Sector", histVars = "Emi|CO|Industrial Sector", vlines = 2020)
```

### Emi|CO|Energy|Demand|Buildings
```{r CO Emissions - Buildings}
showLinePlots(data, "Emi|CO|Energy|Demand|Buildings", histVars = "Emi|CO|Residential Commercial Other", vlines = 2020)
```

### Emi|CO|Product Use|Solvents
```{r CO Emissions - Solvents}
showLinePlots(data, "Emi|CO|Product Use|Solvents", histVars = "Emi|CO|Product Use|Solvents Production and Application", vlines = 2020)
```

### Emi|CO|w/o Bunkers|Energy|Demand|Transport
```{r CO Emissions - Transport}
showLinePlots(data, "Emi|CO|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|CO|Transportation Sector", vlines = 2020)
```

### Emi|CO|Waste
```{r CO Emissions - Waste}
showLinePlots(data, "Emi|CO|Waste", histVars = "Emi|CO|Waste", vlines = 2020)
```


## NH3

### Emi|NH3|REMIND total
```{r NH3 Emissions - REMIND Total}
showLinePlots(data, "Emi|NH3|REMIND total", histVars = "Emi|NH3|REMIND total", vlines = 2020)
```

### Emi|NH3|Extra|Energy|Demand|Transport|Pass|Aviation
```{r NH3 Emissions - Aviation}
showLinePlots(data, "Emi|NH3|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|NH3|Aircraft", vlines = 2020)
```

### Emi|NH3|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r NH3 Emissions - International Shipping}
showLinePlots(data, "Emi|NH3|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|NH3|International Shipping", vlines = 2020)
```

### Emi|NH3|Energy|Supply
```{r NH3 Emissions - Energy Supply}
showLinePlots(data, "Emi|NH3|Energy|Supply", histVars = "Emi|NH3|Energy Sector", vlines = 2020)
```

### Emi|NH3|Industrial Sector
```{r NH3 Emissions - Industry}
showLinePlots(data, "Emi|NH3|Industrial Sector", histVars = "Emi|NH3|Industrial Sector", vlines = 2020)
```

### Emi|NH3|Energy|Demand|Buildings
```{r NH3 Emissions - Buildings}
showLinePlots(data, "Emi|NH3|Energy|Demand|Buildings", histVars = "Emi|NH3|Residential Commercial Other", vlines = 2020)
```

### Emi|NH3|Product Use|Solvents
```{r NH3 Emissions - Solvents}
showLinePlots(data, "Emi|NH3|Product Use|Solvents", histVars = "Emi|NH3|Product Use|Solvents Production and Application", vlines = 2020)
```

### Emi|NH3|w/o Bunkers|Energy|Demand|Transport
```{r NH3 Emissions - Transport}
showLinePlots(data, "Emi|NH3|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|NH3|Transportation Sector", vlines = 2020)
```

### Emi|NH3|Waste
```{r NH3 Emissions - Waste}
showLinePlots(data, "Emi|NH3|Waste", histVars = "Emi|NH3|Waste", vlines = 2020)
```


## NOx

### Emi|NOx|REMIND total
```{r NOx Emissions - REMIND Total}
showLinePlots(data, "Emi|NOx|REMIND total", histVars = "Emi|NOX|REMIND total", vlines = 2020)
```

### Emi|NOx|Extra|Energy|Demand|Transport|Pass|Aviation
```{r NOx Emissions - Aviation}
showLinePlots(data, "Emi|NOx|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|NOX|Aircraft", vlines = 2020)
```

### Emi|NOx|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r NOx Emissions - International Shipping}
showLinePlots(data, "Emi|NOx|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|NOX|International Shipping", vlines = 2020)
```

### Emi|NOx|Energy|Supply
```{r NOx Emissions - Energy Supply}
showLinePlots(data, "Emi|NOx|Energy|Supply", histVars = "Emi|NOX|Energy Sector", vlines = 2020)
```

### Emi|NOx|Industrial Sector
```{r NOx Emissions - Industry}
showLinePlots(data, "Emi|NOx|Industrial Sector", histVars = "Emi|NOX|Industrial Sector", vlines = 2020)
```

### Emi|NOx|Energy|Demand|Buildings
```{r NOx Emissions - Buildings}
showLinePlots(data, "Emi|NOx|Energy|Demand|Buildings", histVars = "Emi|NOX|Residential Commercial Other", vlines = 2020)
```

### Emi|NOx|Product Use|Solvents
```{r NOx Emissions - Solvents}
showLinePlots(data, "Emi|NOx|Product Use|Solvents", histVars = "Emi|NOX|Product Use|Solvents Production and Application", vlines = 2020)
```

### Emi|NOx|w/o Bunkers|Energy|Demand|Transport
```{r NOx Emissions - Transport}
showLinePlots(data, "Emi|NOx|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|NOX|Transportation Sector", vlines = 2020)
```

### Emi|NOx|Waste
```{r NOx Emissions - Waste}
showLinePlots(data, "Emi|NOx|Waste", histVars = "Emi|NOX|Waste", vlines = 2020)
```

## OC

### Emi|OC|REMIND total
```{r OC Emissions - REMIND Total}
showLinePlots(data, "Emi|OC|REMIND total", histVars = "Emi|OC|REMIND total", vlines = 2020)
```

### Emi|OC|Extra|Energy|Demand|Transport|Pass|Aviation
```{r OC Emissions - Aviation}
showLinePlots(data, "Emi|OC|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|OC|Aircraft", vlines = 2020)
```

### Emi|OC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r OC Emissions - International Shipping}
showLinePlots(data, "Emi|OC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|OC|International Shipping", vlines = 2020)
```

### Emi|OC|Energy|Supply
```{r OC Emissions - Energy Supply}
showLinePlots(data, "Emi|OC|Energy|Supply", histVars = "Emi|OC|Energy Sector", vlines = 2020)
```

### Emi|OC|Industrial Sector
```{r OC Emissions - Industry}
showLinePlots(data, "Emi|OC|Industrial Sector", histVars = "Emi|OC|Industrial Sector", vlines = 2020)
```

### Emi|OC|Energy|Demand|Buildings
```{r OC Emissions - Buildings}
showLinePlots(data, "Emi|OC|Energy|Demand|Buildings", histVars = "Emi|OC|Residential Commercial Other", vlines = 2020)
```

### Emi|OC|Product Use|Solvents
```{r OC Emissions - Solvents}
showLinePlots(data, "Emi|OC|Product Use|Solvents", histVars = "Emi|OC|Product Use|Solvents Production and Application", vlines = 2020)
```

### Emi|OC|w/o Bunkers|Energy|Demand|Transport
```{r OC Emissions - Transport}
showLinePlots(data, "Emi|OC|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|OC|Transportation Sector", vlines = 2020)
```

### Emi|OC|Waste
```{r OC Emissions - Waste}
showLinePlots(data, "Emi|OC|Waste", histVars = "Emi|OC|Waste", vlines = 2020)
```

## SO2

### Emi|SO2|REMIND total
```{r SO2 Emissions - REMIND Total}
showLinePlots(data, "Emi|SO2|REMIND total", histVars = "Emi|Sulfur|REMIND total", vlines = 2020)
```

### Emi|SO2|Extra|Energy|Demand|Transport|Pass|Aviation
```{r SO2 Emissions - Aviation}
showLinePlots(data, "Emi|SO2|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|Sulfur|Aircraft", vlines = 2020)
```

### Emi|SO2|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r SO2 Emissions - International Shipping}
showLinePlots(data, "Emi|SO2|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|Sulfur|International Shipping", vlines = 2020)
```

### Emi|SO2|Energy|Supply
```{r SO2 Emissions - Energy Supply}
showLinePlots(data, "Emi|SO2|Energy|Supply", histVars = "Emi|Sulfur|Energy Sector", vlines = 2020)
```

### Emi|SO2|Industrial Sector
```{r SO2 Emissions - Industry}
showLinePlots(data, "Emi|SO2|Industrial Sector", histVars = "Emi|Sulfur|Industrial Sector", vlines = 2020)
```

### Emi|SO2|Energy|Demand|Buildings
```{r SO2 Emissions - Buildings}
showLinePlots(data, "Emi|SO2|Energy|Demand|Buildings", histVars = "Emi|Sulfur|Residential Commercial Other", vlines = 2020)
```

### Emi|SO2|Product Use|Solvents
```{r SO2 Emissions - Solvents}
showLinePlots(data, "Emi|SO2|Product Use|Solvents", histVars = "Emi|Sulfur|Product Use|Solvents Production and Application", vlines = 2020)
```

### Emi|SO2|w/o Bunkers|Energy|Demand|Transport
```{r SO2 Emissions - Transport}
showLinePlots(data, "Emi|SO2|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|Sulfur|Transportation Sector", vlines = 2020)
```

### Emi|SO2|Waste
```{r SO2 Emissions - Waste}
showLinePlots(data, "Emi|SO2|Waste", histVars = "Emi|Sulfur|Waste", vlines = 2020)
```


## VOC

### Emi|VOC|REMIND total
```{r VOC Emissions - REMIND Total}
showLinePlots(data, "Emi|VOC|REMIND total", histVars = "Emi|VOC|REMIND total", vlines = 2020)
```

### Emi|VOC|Extra|Energy|Demand|Transport|Pass|Aviation
```{r VOC Emissions - Aviation}
showLinePlots(data, "Emi|VOC|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|VOC|Aircraft", vlines = 2020)
```

### Emi|VOC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping
```{r VOC Emissions - International Shipping}
showLinePlots(data, "Emi|VOC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|VOC|International Shipping", vlines = 2020)
```

### Emi|VOC|Energy|Supply
```{r VOC Emissions - Energy Supply}
showLinePlots(data, "Emi|VOC|Energy|Supply", histVars = "Emi|VOC|Energy Sector", vlines = 2020)
```

### Emi|VOC|Industrial Sector
```{r VOC Emissions - Industry}
showLinePlots(data, "Emi|VOC|Industrial Sector", histVars = "Emi|VOC|Industrial Sector", vlines = 2020)
```

### Emi|VOC|Energy|Demand|Buildings
```{r VOC Emissions - Buildings}
showLinePlots(data, "Emi|VOC|Energy|Demand|Buildings", histVars = "Emi|VOC|Residential Commercial Other", vlines = 2020)
```

### Emi|VOC|Product Use|Solvents
```{r VOC Emissions - Solvents}
showLinePlots(data, "Emi|VOC|Product Use|Solvents", histVars = "Emi|VOC|Product Use|Solvents Production and Application", vlines = 2020)
```

### Emi|VOC|w/o Bunkers|Energy|Demand|Transport
```{r VOC Emissions - Transport}
showLinePlots(data, "Emi|VOC|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|VOC|Transportation Sector", vlines = 2020)
```

### Emi|VOC|Waste
```{r VOC Emissions - Waste}
showLinePlots(data, "Emi|VOC|Waste", histVars = "Emi|VOC|Waste", vlines = 2020)
```
