<!--
|  (C) 2006-2024 Potsdam Institute for Climate Impact Research (PIK)
|  authors, and contributors see CITATION.cff file. This file is part
|  of REMIND and licensed under AGPL-3.0-or-later. Under Section 7 of
|  AGPL-3.0, you are granted additional permissions described in the
|  REMIND License Exception, version 1.0 (see LICENSE file).
|  Contact: remind@pik-potsdam.de
-->
# CMIP7 Emissions

This document provides an overview of the emissions in REMIND and MAgPIE at the sectoral resolution that is used for the emissions harmonization
in ScenarioMIP for CMIP7. It covers 10 emission species:

1. CO2
2. CH4
3. N2O
4. BC
5. CO
6. NH3
7. NOx
8. OC
9. SO2
10. VOC

It covers 13 sectors, of which 5 are provided by MAgPIE:

1. Agricultural Waste Burning
2. Agriculture
3. Forest Burning
4. Grassland Burning
5. Peat Burning

8 sectors are provided by REMIND:

1. Aircraft
2. International Shipping
3. Energy Sector
4. Industrial Sector
5. Residential Commercial Other
6. Solvents Production and Application
7. Transportation Sector
8. Waste

Historical emissions based on CEDS, GFED and GCB (for CO2 AFOLU) up to 2023 are those used in the emissions harmonization in ScenarioMIP for CMIP7.

```{r, echo = FALSE, results = 'hide'}
# Adds a new variable as the sum of a list of variables
addSumVariables <- function(
  fdata, sumvars, outvarname, outunit = NULL, convmult = 1, convoffset = 0, only.new = FALSE
  ) {
  if (is.null(outunit)) {
    outunit <- fdata %>%
      filter(variable == sumvars[1]) %>%
      slice(1) %>%
      select(unit) %>% unlist %>% as.character
  }

  newdata <- fdata %>%
    filter(variable %in% sumvars) %>%
    select(-varplus) %>%
    distinct %>%
    pivot_wider(names_from = variable, values_from = value) %>%
    mutate(value = rowSums(across(sumvars))) %>%
    select(-c(sumvars)) %>%
    mutate(variable = outvarname, varplus = outvarname, unit = outunit)
  if(!only.new) {
    return(rbind(fdata, newdata))
  } else {
    return(newdata)
  }
}
```

```{r, echo = FALSE, results = 'hide'}
# Compute emissions for CMIP7 industrial sector from REMIND
for (species in c("BC", "CO", "NH3", "NOx", "OC", "SO2", "VOC")) {
  sumvars <- c(
    paste0("Emi|", species, "|Energy|Demand|Industry"),
    paste0("Emi|", species, "|Industrial Processes")
  )
  
  data <- data %>% 
    filter(model == "REMIND") %>%
    addSumVariables(sumvars, paste0("Emi|", species,"|Industrial Sector"), only.new = TRUE) %>%
    bind_rows(data)
}

# Compute CO2 emissions for CMIP7 aircraft sector from REMIND
data <- data %>%
  filter(model == "REMIND") %>%
  addSumVariables(c("Emi|CO2|Energy|Demand|Transport|Pass|Domestic Aviation",
                    "Emi|CO2|Energy|Demand|Transport|Bunkers|Pass|International Aviation"),
                  "Emi|CO2|Energy|Demand|Transport|Pass|Aviation", only.new = TRUE) %>%
  bind_rows(data)

```


# CO2
For CO2 emissions, the emissions harmonization in CMIP7 has the additional sectors BECCS, Biochar, Direct Air Capture, Enhanced Weathering, Ocean, Other CDR, and Soil Carbon Management.
These are included in the total *Emi|CO2|w/ Bunkers*, but we do not separately show the sectors below since the historical emissions are equal to zero for these sectors.

## Emi|CO2
The variable *Emi|CO2|w/ Bunkers* does **not** include *Emissions|CO2|Land|Biomass Burning|Burning of Crop Residues* since this variable is only available in MAgPIE, not in REMIND.
```{r CO2 Emissions}
showLinePlots(data, "Emi|CO2|w/ Bunkers", histVars = "Emi|CMIP7|CO2", vlines = 2020)
```

## MAgPIE
CO2 emissions from land-use change are only harmonized at the global level in CMIP7 for use in Simple Climate Models. Historical emissions are based on the Global Carbon Budget (GCB).

IAMs do not report CO2 emissions from forest burning, grassland burning and peat burning in CMIP7.

### Emi|CO2|Land-Use Change (CMIP7 sector: AFOLU)
```{r CO2 Emissions - Agriculture}
showLinePlots(data, "Emi|CO2|Land-Use Change", histVars = "Emi|CMIP7|CO2|AFOLU", vlines = 2020)
```

### Emissions|CO2|Land|Biomass Burning|Burning of Crop Residues (CMIP7 sector: Agricultural Waste Burning)

This variable is only available in MAgPIE, not in REMIND. Thus, it cannot be reported for REMIND standalone runs and is **not** included in *Emi|CO2|w/ Bunkers*.
```{r CO2 Emissions - Agricultural Waste Burning}
showLinePlots(data, "Emissions|CO2|Land|Biomass Burning|Burning of Crop Residues", histVars = "Emi|CO2|AFOLU|Agricultural Waste Burning", vlines = 2020)
```

## REMIND
CO2 emissions from solvents production and application are not modelled in REMIND.

### Emi|CO2|Energy|Demand|Transport|Pass|Aviation (CMIP7 sector: Aircraft)
```{r CO2 Emissions - Aircraft}
showLinePlots(data, "Emi|CO2|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|CO2|Energy|Demand|Transport|Pass|Aviation", vlines = 2020)
```

### Emi|CO2|Energy|Demand|Transport|Bunkers|Freight|International Shipping (CMIP7 sector: International Shipping)
```{r CO2 Emissions - International Shipping}
showLinePlots(data, "Emi|CO2|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|CO2|Energy|Demand|Transport|Bunkers|Freight|International Shipping", vlines = 2020)
```

### Emi|CO2|Energy|Supply (CMIP7 sector: Energy Sector)
```{r CO2 Emissions - Energy Sector}
showLinePlots(data, "Emi|CO2|Energy|Supply", histVars = "Emi|CO2|Energy|Supply", vlines = 2020)
```

### Emi|CO2|Industry (CMIP7 sector: Industrial Sector)
*Emi|CO2|Industry* is the sum of *Emi|CO2|Energy|Demand|+|Industry* and *Emi|CO2|Industrial Processes|+|Industry*.

```{r CO2 Emissions - Industrial Sector}
showLinePlots(data, "Emi|CO2|Industry", histVars = "Emi|CO2|Industry", vlines = 2020)
```

### Emi|CO2|Energy|Demand|Buildings (CMIP7 sector: Residential Commercial Other)
```{r CO2 Emissions - Residential Commercial Other}
showLinePlots(data, "Emi|CO2|Energy|Demand|Buildings", histVars = "Emi|CO2|Energy|Demand|Buildings", vlines = 2020)
```

### Emi|CO2|w/o Bunkers|Energy|Demand|Transport (CMIP7 sector: Transportation Sector)
```{r CO2 Emissions - Transportation Sector}
showLinePlots(data, "Emi|CO2|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|CO2|w/o Bunkers|Energy|Demand|Transport", vlines = 2020)
```

### Emi|CO2|Waste (CMIP7 sector: Waste)
```{r CO2 Emissions - Waste}
showLinePlots(data, "Emi|CO2|Waste", histVars = "Emi|CO2|Waste", vlines = 2020)
```

# CH4 and N2O
Reporting of CH4 and N2O emissions in ScenarioMIP for CMIP7 (using mapping_ScenarioMIP.csv) currently relies on a combination of various REMIND and MAgPIE variables 
since the REMIND totals do not correctly reflect all MAgPIE CH4 emissions and some REMIND variables are only computed in the postprocessing as part of *remind2::reportExtraEmissions*.

TODO: Clean-up handling of CH4 and N2O emissions in REMIND and in piamInterfaces (mapping_ScenarioMIP) to ensure correct reporting for REMIND standalone and REMIND-MAgPIE coupled runs.

# BC
```{r BC Emissions}
showLinePlots(data, "Emi|BC|w/ Bunkers", histVars = "Emi|BC", vlines = 2020)
```

## MAgPIE

### Emi|BC|AFOLU|Agricultural Waste Burning (CMIP7 sector: Agricultural Waste Burning)
```{r BC Emissions - Agricultural Waste Burning}
showLinePlots(data, "Emi|BC|AFOLU|Agricultural Waste Burning", histVars = "Emi|BC|AFOLU|Agricultural Waste Burning", vlines = 2020)
```

### Emi|BC|AFOLU|Agriculture (CMIP7 sector: Agriculture)
```{r BC Emissions - Agriculture}
showLinePlots(data, "Emi|BC|AFOLU|Agriculture", histVars = "Emi|BC|Agriculture", vlines = 2020)
```

### Emi|BC|AFOLU|Land|Fires|Forest Burning (CMIP7 sector: Forest Burning)
```{r BC Emissions - Forest Burning}
showLinePlots(data, "Emi|BC|AFOLU|Land|Fires|Forest Burning", histVars = "Emi|BC|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emi|BC|AFOLU|Land|Fires|Grassland Burning (CMIP7 sector: Grassland Burning)
```{r BC Emissions - Grassland Burning}
showLinePlots(data, "Emi|BC|AFOLU|Land|Fires|Grassland Burning", histVars = "Emi|BC|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emi|BC|AFOLU|Land|Fires|Peat Burning (CMIP7 sector: Peat Burning)
```{r BC Emissions - Peat Burning}
showLinePlots(data, "Emi|BC|AFOLU|Land|Fires|Peat Burning", histVars = "Emi|BC|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

## REMIND

### Emi|BC|Extra|Energy|Demand|Transport|Pass|Aviation (CMIP7 sector: Aircraft)
```{r BC Emissions - Aircraft}
showLinePlots(data, "Emi|BC|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|BC|Energy|Demand|Transport|Pass|Aviation", vlines = 2020)
```

### Emi|BC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping (CMIP7 sector: International Shipping)
```{r BC Emissions - International Shipping}
showLinePlots(data, "Emi|BC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|BC|Energy|Demand|Transport|Bunkers|Freight|International Shipping", vlines = 2020)
```

### Emi|BC|Energy|Supply (CMIP7 sector: Energy Sector)
```{r BC Emissions - Energy Sector}
showLinePlots(data, "Emi|BC|Energy|Supply", histVars = "Emi|BC|Energy|Supply", vlines = 2020)
```

### Emi|BC|Industrial Sector (CMIP7 sector: Industrial Sector)
```{r BC Emissions - Industrial Sector}
showLinePlots(data, "Emi|BC|Industrial Sector", histVars = "Emi|BC|Industry", vlines = 2020)
```

### Emi|BC|Energy|Demand|Buildings (CMIP7 sector: Residential Commercial Other)
```{r BC Emissions - Residential Commercial Other}
showLinePlots(data, "Emi|BC|Energy|Demand|Buildings", histVars = "Emi|BC|Energy|Demand|Buildings", vlines = 2020)
```

### Emi|BC|Product Use|Solvents (CMIP7 sector: Solvents Production and Application)
```{r BC Emissions - Solvents Production and Application}
showLinePlots(data, "Emi|BC|Product Use|Solvents", histVars = "Emi|BC|Product Use|Solvents", vlines = 2020)
```

### Emi|BC|w/o Bunkers|Energy|Demand|Transport (CMIP7 sector: Transportation Sector)
```{r BC Emissions - Transportation Sector}
showLinePlots(data, "Emi|BC|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|BC|w/o Bunkers|Energy|Demand|Transport", vlines = 2020)
```

### Emi|BC|Waste (CMIP7 sector: Waste)
```{r BC Emissions - Waste}
showLinePlots(data, "Emi|BC|Waste", histVars = "Emi|BC|Waste", vlines = 2020)
```

# CO
```{r CO Emissions}
showLinePlots(data, "Emi|CO|w/ Bunkers", histVars = "Emi|CO", vlines = 2020)
```

## MAgPIE

### Emi|CO|AFOLU|Agricultural Waste Burning (CMIP7 sector: Agricultural Waste Burning)
```{r CO Emissions - Agricultural Waste Burning}
showLinePlots(data, "Emi|CO|AFOLU|Agricultural Waste Burning", histVars = "Emi|CO|AFOLU|Agricultural Waste Burning", vlines = 2020)
```

### Emi|CO|AFOLU|Agriculture (CMIP7 sector: Agriculture)
```{r CO Emissions - Agriculture}
showLinePlots(data, "Emi|CO|AFOLU|Agriculture", histVars = "Emi|CO|Agriculture", vlines = 2020)
```

### Emi|CO|AFOLU|Land|Fires|Forest Burning (CMIP7 sector: Forest Burning)
```{r CO Emissions - Forest Burning}
showLinePlots(data, "Emi|CO|AFOLU|Land|Fires|Forest Burning", histVars = "Emi|CO|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emi|CO|AFOLU|Land|Fires|Grassland Burning (CMIP7 sector: Grassland Burning)
```{r CO Emissions - Grassland Burning}
showLinePlots(data, "Emi|CO|AFOLU|Land|Fires|Grassland Burning", histVars = "Emi|CO|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emi|CO|AFOLU|Land|Fires|Peat Burning (CMIP7 sector: Peat Burning)
```{r CO Emissions - Peat Burning}
showLinePlots(data, "Emi|CO|AFOLU|Land|Fires|Peat Burning", histVars = "Emi|CO|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

## REMIND

### Emi|CO|Extra|Energy|Demand|Transport|Pass|Aviation (CMIP7 sector: Aircraft)
```{r CO Emissions - Aircraft}
showLinePlots(data, "Emi|CO|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|CO|Energy|Demand|Transport|Pass|Aviation", vlines = 2020)
```

### Emi|CO|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping (CMIP7 sector: International Shipping)
```{r CO Emissions - International Shipping}
showLinePlots(data, "Emi|CO|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|CO|Energy|Demand|Transport|Bunkers|Freight|International Shipping", vlines = 2020)
```

### Emi|CO|Energy|Supply (CMIP7 sector: Energy Sector)
```{r CO Emissions - Energy Sector}
showLinePlots(data, "Emi|CO|Energy|Supply", histVars = "Emi|CO|Energy|Supply", vlines = 2020)
```

### Emi|CO|Industrial Sector (CMIP7 sector: Industrial Sector)
```{r CO Emissions - Industrial Sector}
showLinePlots(data, "Emi|CO|Industrial Sector", histVars = "Emi|CO|Industry", vlines = 2020)
```

### Emi|CO|Energy|Demand|Buildings (CMIP7 sector: Residential Commercial Other)
```{r CO Emissions - Residential Commercial Other}
showLinePlots(data, "Emi|CO|Energy|Demand|Buildings", histVars = "Emi|CO|Energy|Demand|Buildings", vlines = 2020)
```

### Emi|CO|Product Use|Solvents (CMIP7 sector: Solvents Production and Application)
```{r CO Emissions - Solvents Production and Application}
showLinePlots(data, "Emi|CO|Product Use|Solvents", histVars = "Emi|CO|Product Use|Solvents", vlines = 2020)
```

### Emi|CO|w/o Bunkers|Energy|Demand|Transport (CMIP7 sector: Transportation Sector)
```{r CO Emissions - Transportation Sector}
showLinePlots(data, "Emi|CO|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|CO|w/o Bunkers|Energy|Demand|Transport", vlines = 2020)
```

### Emi|CO|Waste (CMIP7 sector: Waste)
```{r CO Emissions - Waste}
showLinePlots(data, "Emi|CO|Waste", histVars = "Emi|CO|Waste", vlines = 2020)
```

# NH3
```{r NH3 Emissions}
showLinePlots(data, "Emi|NH3|w/ Bunkers", histVars = "Emi|NH3", vlines = 2020)
```

## MAgPIE

### Emi|NH3|AFOLU|Agricultural Waste Burning (CMIP7 sector: Agricultural Waste Burning)
```{r NH3 Emissions - Agricultural Waste Burning}
showLinePlots(data, "Emi|NH3|AFOLU|Agricultural Waste Burning", histVars = "Emi|NH3|AFOLU|Agricultural Waste Burning", vlines = 2020)
```

### Emi|NH3|AFOLU|Agriculture (CMIP7 sector: Agriculture)
```{r NH3 Emissions - Agriculture}
showLinePlots(data, "Emi|NH3|AFOLU|Agriculture", histVars = "Emi|NH3|Agriculture", vlines = 2020)
```

### Emi|NH3|AFOLU|Land|Fires|Forest Burning (CMIP7 sector: Forest Burning)
```{r NH3 Emissions - Forest Burning}
showLinePlots(data, "Emi|NH3|AFOLU|Land|Fires|Forest Burning", histVars = "Emi|NH3|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emi|NH3|AFOLU|Land|Fires|Grassland Burning (CMIP7 sector: Grassland Burning)
```{r NH3 Emissions - Grassland Burning}
showLinePlots(data, "Emi|NH3|AFOLU|Land|Fires|Grassland Burning", histVars = "Emi|NH3|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emi|NH3|AFOLU|Land|Fires|Peat Burning (CMIP7 sector: Peat Burning)
```{r NH3 Emissions - Peat Burning}
showLinePlots(data, "Emi|NH3|AFOLU|Land|Fires|Peat Burning", histVars = "Emi|NH3|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

## REMIND

### Emi|NH3|Extra|Energy|Demand|Transport|Pass|Aviation (CMIP7 sector: Aircraft)
```{r NH3 Emissions - Aircraft}
showLinePlots(data, "Emi|NH3|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|NH3|Energy|Demand|Transport|Pass|Aviation", vlines = 2020)
```

### Emi|NH3|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping (CMIP7 sector: International Shipping)
```{r NH3 Emissions - International Shipping}
showLinePlots(data, "Emi|NH3|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|NH3|Energy|Demand|Transport|Bunkers|Freight|International Shipping", vlines = 2020)
```

### Emi|NH3|Energy|Supply (CMIP7 sector: Energy Sector)
```{r NH3 Emissions - Energy Sector}
showLinePlots(data, "Emi|NH3|Energy|Supply", histVars = "Emi|NH3|Energy|Supply", vlines = 2020)
```

### Emi|NH3|Industrial Sector (CMIP7 sector: Industrial Sector)
```{r NH3 Emissions - Industrial Sector}
showLinePlots(data, "Emi|NH3|Industrial Sector", histVars = "Emi|NH3|Industry", vlines = 2020)
```

### Emi|NH3|Energy|Demand|Buildings (CMIP7 sector: Residential Commercial Other)
```{r NH3 Emissions - Residential Commercial Other}
showLinePlots(data, "Emi|NH3|Energy|Demand|Buildings", histVars = "Emi|NH3|Energy|Demand|Buildings", vlines = 2020)
```

### Emi|NH3|Product Use|Solvents (CMIP7 sector: Solvents Production and Application)
```{r NH3 Emissions - Solvents Production and Application}
showLinePlots(data, "Emi|NH3|Product Use|Solvents", histVars = "Emi|NH3|Product Use|Solvents", vlines = 2020)
```

### Emi|NH3|w/o Bunkers|Energy|Demand|Transport (CMIP7 sector: Transportation Sector)
```{r NH3 Emissions - Transportation Sector}
showLinePlots(data, "Emi|NH3|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|NH3|w/o Bunkers|Energy|Demand|Transport", vlines = 2020)
```

### Emi|NH3|Waste (CMIP7 sector: Waste)
```{r NH3 Emissions - Waste}
showLinePlots(data, "Emi|NH3|Waste", histVars = "Emi|NH3|Waste", vlines = 2020)
```

# NOx
```{r NOx Emissions}
showLinePlots(data, "Emi|NOx|w/ Bunkers", histVars = "Emi|NOX", vlines = 2020)
```

## MAgPIE

### Emi|NOx|AFOLU|Agricultural Waste Burning (CMIP7 sector: Agricultural Waste Burning)
```{r NOx Emissions - Agricultural Waste Burning}
showLinePlots(data, "Emi|NOx|AFOLU|Agricultural Waste Burning", histVars = "Emi|NOX|AFOLU|Agricultural Waste Burning", vlines = 2020)
```

### Emi|NOx|AFOLU|Agriculture (CMIP7 sector: Agriculture)
```{r NOx Emissions - Agriculture}
showLinePlots(data, "Emi|NOx|AFOLU|Agriculture", histVars = "Emi|NOX|Agriculture", vlines = 2020)
```

### Emi|NOx|AFOLU|Land|Fires|Forest Burning (CMIP7 sector: Forest Burning)
```{r NOx Emissions - Forest Burning}
showLinePlots(data, "Emi|NOx|AFOLU|Land|Fires|Forest Burning", histVars = "Emi|NOX|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emi|NOx|AFOLU|Land|Fires|Grassland Burning (CMIP7 sector: Grassland Burning)
```{r NOx Emissions - Grassland Burning}
showLinePlots(data, "Emi|NOx|AFOLU|Land|Fires|Grassland Burning", histVars = "Emi|NOX|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emi|NOx|AFOLU|Land|Fires|Peat Burning (CMIP7 sector: Peat Burning)
```{r NOx Emissions - Peat Burning}
showLinePlots(data, "Emi|NOx|AFOLU|Land|Fires|Peat Burning", histVars = "Emi|NOX|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

## REMIND

### Emi|NOx|Extra|Energy|Demand|Transport|Pass|Aviation (CMIP7 sector: Aircraft)
```{r NOx Emissions - Aircraft}
showLinePlots(data, "Emi|NOx|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|NOX|Energy|Demand|Transport|Pass|Aviation", vlines = 2020)
```

### Emi|NOx|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping (CMIP7 sector: International Shipping)
```{r NOx Emissions - International Shipping}
showLinePlots(data, "Emi|NOx|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|NOX|Energy|Demand|Transport|Bunkers|Freight|International Shipping", vlines = 2020)
```

### Emi|NOx|Energy|Supply (CMIP7 sector: Energy Sector)
```{r NOx Emissions - Energy Sector}
showLinePlots(data, "Emi|NOx|Energy|Supply", histVars = "Emi|NOX|Energy|Supply", vlines = 2020)
```

### Emi|NOx|Industrial Sector (CMIP7 sector: Industrial Sector)
```{r NOx Emissions - Industrial Sector}
showLinePlots(data, "Emi|NOx|Industrial Sector", histVars = "Emi|NOX|Industry", vlines = 2020)
```

### Emi|NOx|Energy|Demand|Buildings (CMIP7 sector: Residential Commercial Other)
```{r NOx Emissions - Residential Commercial Other}
showLinePlots(data, "Emi|NOx|Energy|Demand|Buildings", histVars = "Emi|NOX|Energy|Demand|Buildings", vlines = 2020)
```

### Emi|NOx|Product Use|Solvents (CMIP7 sector: Solvents Production and Application)
```{r NOx Emissions - Solvents Production and Application}
showLinePlots(data, "Emi|NOx|Product Use|Solvents", histVars = "Emi|NOX|Product Use|Solvents", vlines = 2020)
```

### Emi|NOx|w/o Bunkers|Energy|Demand|Transport (CMIP7 sector: Transportation Sector)
```{r NOx Emissions - Transportation Sector}
showLinePlots(data, "Emi|NOx|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|NOX|w/o Bunkers|Energy|Demand|Transport", vlines = 2020)
```

### Emi|NOx|Waste (CMIP7 sector: Waste)
```{r NOx Emissions - Waste}
showLinePlots(data, "Emi|NOx|Waste", histVars = "Emi|NOX|Waste", vlines = 2020)
```

# OC
```{r OC Emissions}
showLinePlots(data, "Emi|OC|w/ Bunkers", histVars = "Emi|OC", vlines = 2020)
```

## MAgPIE

### Emi|OC|AFOLU|Agricultural Waste Burning (CMIP7 sector: Agricultural Waste Burning)
```{r OC Emissions - Agricultural Waste Burning}
showLinePlots(data, "Emi|OC|AFOLU|Agricultural Waste Burning", histVars = "Emi|OC|AFOLU|Agricultural Waste Burning", vlines = 2020)
```

### Emi|OC|AFOLU|Agriculture (CMIP7 sector: Agriculture)
```{r OC Emissions - Agriculture}
showLinePlots(data, "Emi|OC|AFOLU|Agriculture", histVars = "Emi|OC|Agriculture", vlines = 2020)
```

### Emi|OC|AFOLU|Land|Fires|Forest Burning (CMIP7 sector: Forest Burning)
```{r OC Emissions - Forest Burning}
showLinePlots(data, "Emi|OC|AFOLU|Land|Fires|Forest Burning", histVars = "Emi|OC|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emi|OC|AFOLU|Land|Fires|Grassland Burning (CMIP7 sector: Grassland Burning)
```{r OC Emissions - Grassland Burning}
showLinePlots(data, "Emi|OC|AFOLU|Land|Fires|Grassland Burning", histVars = "Emi|OC|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emi|OC|AFOLU|Land|Fires|Peat Burning (CMIP7 sector: Peat Burning)
```{r OC Emissions - Peat Burning}
showLinePlots(data, "Emi|OC|AFOLU|Land|Fires|Peat Burning", histVars = "Emi|OC|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

## REMIND

### Emi|OC|Extra|Energy|Demand|Transport|Pass|Aviation (CMIP7 sector: Aircraft)
```{r OC Emissions - Aircraft}
showLinePlots(data, "Emi|OC|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|OC|Energy|Demand|Transport|Pass|Aviation", vlines = 2020)
```

### Emi|OC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping (CMIP7 sector: International Shipping)
```{r OC Emissions - International Shipping}
showLinePlots(data, "Emi|OC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|OC|Energy|Demand|Transport|Bunkers|Freight|International Shipping", vlines = 2020)
```

### Emi|OC|Energy|Supply (CMIP7 sector: Energy Sector)
```{r OC Emissions - Energy Sector}
showLinePlots(data, "Emi|OC|Energy|Supply", histVars = "Emi|OC|Energy|Supply", vlines = 2020)
```

### Emi|OC|Industrial Sector (CMIP7 sector: Industrial Sector)
```{r OC Emissions - Industrial Sector}
showLinePlots(data, "Emi|OC|Industrial Sector", histVars = "Emi|OC|Industry", vlines = 2020)
```

### Emi|OC|Energy|Demand|Buildings (CMIP7 sector: Residential Commercial Other)
```{r OC Emissions - Residential Commercial Other}
showLinePlots(data, "Emi|OC|Energy|Demand|Buildings", histVars = "Emi|OC|Energy|Demand|Buildings", vlines = 2020)
```

### Emi|OC|Product Use|Solvents (CMIP7 sector: Solvents Production and Application)
```{r OC Emissions - Solvents Production and Application}
showLinePlots(data, "Emi|OC|Product Use|Solvents", histVars = "Emi|OC|Product Use|Solvents", vlines = 2020)
```

### Emi|OC|w/o Bunkers|Energy|Demand|Transport (CMIP7 sector: Transportation Sector)
```{r OC Emissions - Transportation Sector}
showLinePlots(data, "Emi|OC|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|OC|w/o Bunkers|Energy|Demand|Transport", vlines = 2020)
```

### Emi|OC|Waste (CMIP7 sector: Waste)
```{r OC Emissions - Waste}
showLinePlots(data, "Emi|OC|Waste", histVars = "Emi|OC|Waste", vlines = 2020)
```

# SO2
```{r SO2 Emissions}
showLinePlots(data, "Emi|SO2|w/ Bunkers", histVars = "Emi|SO2", vlines = 2020)
```

## MAgPIE

### Emi|SO2|AFOLU|Agricultural Waste Burning (CMIP7 sector: Agricultural Waste Burning)
```{r SO2 Emissions - Agricultural Waste Burning}
showLinePlots(data, "Emi|SO2|AFOLU|Agricultural Waste Burning", histVars = "Emi|SO2|AFOLU|Agricultural Waste Burning", vlines = 2020)
```

### Emi|SO2|AFOLU|Agriculture (CMIP7 sector: Agriculture)
```{r SO2 Emissions - Agriculture}
showLinePlots(data, "Emi|SO2|AFOLU|Agriculture", histVars = "Emi|SO2|Agriculture", vlines = 2020)
```

### Emi|SO2|AFOLU|Land|Fires|Forest Burning (CMIP7 sector: Forest Burning)
```{r SO2 Emissions - Forest Burning}
showLinePlots(data, "Emi|SO2|AFOLU|Land|Fires|Forest Burning", histVars = "Emi|SO2|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emi|SO2|AFOLU|Land|Fires|Grassland Burning (CMIP7 sector: Grassland Burning)
```{r SO2 Emissions - Grassland Burning}
showLinePlots(data, "Emi|SO2|AFOLU|Land|Fires|Grassland Burning", histVars = "Emi|SO2|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emi|SO2|AFOLU|Land|Fires|Peat Burning (CMIP7 sector: Peat Burning)
```{r SO2 Emissions - Peat Burning}
showLinePlots(data, "Emi|SO2|AFOLU|Land|Fires|Peat Burning", histVars = "Emi|SO2|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

## REMIND

### Emi|SO2|Extra|Energy|Demand|Transport|Pass|Aviation (CMIP7 sector: Aircraft)
```{r SO2 Emissions - Aircraft}
showLinePlots(data, "Emi|SO2|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|SO2|Energy|Demand|Transport|Pass|Aviation", vlines = 2020)
```

### Emi|SO2|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping (CMIP7 sector: International Shipping)
```{r SO2 Emissions - International Shipping}
showLinePlots(data, "Emi|SO2|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|SO2|Energy|Demand|Transport|Bunkers|Freight|International Shipping", vlines = 2020)
```

### Emi|SO2|Energy|Supply (CMIP7 sector: Energy Sector)
```{r SO2 Emissions - Energy Sector}
showLinePlots(data, "Emi|SO2|Energy|Supply", histVars = "Emi|SO2|Energy|Supply", vlines = 2020)
```

### Emi|SO2|Industrial Sector (CMIP7 sector: Industrial Sector)
```{r SO2 Emissions - Industrial Sector}
showLinePlots(data, "Emi|SO2|Industrial Sector", histVars = "Emi|SO2|Industry", vlines = 2020)
```

### Emi|SO2|Energy|Demand|Buildings (CMIP7 sector: Residential Commercial Other)
```{r SO2 Emissions - Residential Commercial Other}
showLinePlots(data, "Emi|SO2|Energy|Demand|Buildings", histVars = "Emi|SO2|Energy|Demand|Buildings", vlines = 2020)
```

### Emi|SO2|Product Use|Solvents (CMIP7 sector: Solvents Production and Application)
```{r SO2 Emissions - Solvents Production and Application}
showLinePlots(data, "Emi|SO2|Product Use|Solvents", histVars = "Emi|SO2|Product Use|Solvents", vlines = 2020)
```

### Emi|SO2|w/o Bunkers|Energy|Demand|Transport (CMIP7 sector: Transportation Sector)
```{r SO2 Emissions - Transportation Sector}
showLinePlots(data, "Emi|SO2|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|SO2|w/o Bunkers|Energy|Demand|Transport", vlines = 2020)
```

### Emi|SO2|Waste (CMIP7 sector: Waste)
```{r SO2 Emissions - Waste}
showLinePlots(data, "Emi|SO2|Waste", histVars = "Emi|SO2|Waste", vlines = 2020)
```

# VOC
```{r VOC Emissions}
showLinePlots(data, "Emi|VOC|w/ Bunkers", histVars = "Emi|VOC", vlines = 2020)
```

## MAgPIE

### Emi|VOC|AFOLU|Agricultural Waste Burning (CMIP7 sector: Agricultural Waste Burning)
```{r VOC Emissions - Agricultural Waste Burning}
showLinePlots(data, "Emi|VOC|AFOLU|Agricultural Waste Burning", histVars = "Emi|VOC|AFOLU|Agricultural Waste Burning", vlines = 2020)
```

### Emi|VOC|AFOLU|Agriculture (CMIP7 sector: Agriculture)
```{r VOC Emissions - Agriculture}
showLinePlots(data, "Emi|VOC|AFOLU|Agriculture", histVars = "Emi|VOC|Agriculture", vlines = 2020)
```

### Emi|VOC|AFOLU|Land|Fires|Forest Burning (CMIP7 sector: Forest Burning)
```{r VOC Emissions - Forest Burning}
showLinePlots(data, "Emi|VOC|AFOLU|Land|Fires|Forest Burning", histVars = "Emi|VOC|AFOLU|Land|Fires|Forest Burning", vlines = 2020)
```

### Emi|VOC|AFOLU|Land|Fires|Grassland Burning (CMIP7 sector: Grassland Burning)
```{r VOC Emissions - Grassland Burning}
showLinePlots(data, "Emi|VOC|AFOLU|Land|Fires|Grassland Burning", histVars = "Emi|VOC|AFOLU|Land|Fires|Grassland Burning", vlines = 2020)
```

### Emi|VOC|AFOLU|Land|Fires|Peat Burning (CMIP7 sector: Peat Burning)
```{r VOC Emissions - Peat Burning}
showLinePlots(data, "Emi|VOC|AFOLU|Land|Fires|Peat Burning", histVars = "Emi|VOC|AFOLU|Land|Fires|Peat Burning", vlines = 2020)
``` 

## REMIND

### Emi|VOC|Extra|Energy|Demand|Transport|Pass|Aviation (CMIP7 sector: Aircraft)
```{r VOC Emissions - Aircraft}
showLinePlots(data, "Emi|VOC|Extra|Energy|Demand|Transport|Pass|Aviation", histVars = "Emi|VOC|Energy|Demand|Transport|Pass|Aviation", vlines = 2020)
```

### Emi|VOC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping (CMIP7 sector: International Shipping)
```{r VOC Emissions - International Shipping}
showLinePlots(data, "Emi|VOC|Extra|Energy|Demand|Transport|Bunkers|Freight|International Shipping", histVars = "Emi|VOC|Energy|Demand|Transport|Bunkers|Freight|International Shipping", vlines = 2020)
```

### Emi|VOC|Energy|Supply (CMIP7 sector: Energy Sector)
```{r VOC Emissions - Energy Sector}
showLinePlots(data, "Emi|VOC|Energy|Supply", histVars = "Emi|VOC|Energy|Supply", vlines = 2020)
```

### Emi|VOC|Industrial Sector (CMIP7 sector: Industrial Sector)
```{r VOC Emissions - Industrial Sector}
showLinePlots(data, "Emi|VOC|Industrial Sector", histVars = "Emi|VOC|Industry", vlines = 2020)
```

### Emi|VOC|Energy|Demand|Buildings (CMIP7 sector: Residential Commercial Other)
```{r VOC Emissions - Residential Commercial Other}
showLinePlots(data, "Emi|VOC|Energy|Demand|Buildings", histVars = "Emi|VOC|Energy|Demand|Buildings", vlines = 2020)
```

### Emi|VOC|Product Use|Solvents (CMIP7 sector: Solvents Production and Application)
```{r VOC Emissions - Solvents Production and Application}
showLinePlots(data, "Emi|VOC|Product Use|Solvents", histVars = "Emi|VOC|Product Use|Solvents", vlines = 2020)
```

### Emi|VOC|w/o Bunkers|Energy|Demand|Transport (CMIP7 sector: Transportation Sector)
```{r VOC Emissions - Transportation Sector}
showLinePlots(data, "Emi|VOC|w/o Bunkers|Energy|Demand|Transport", histVars = "Emi|VOC|w/o Bunkers|Energy|Demand|Transport", vlines = 2020)
```

### Emi|VOC|Waste (CMIP7 sector: Waste)
```{r VOC Emissions - Waste}
showLinePlots(data, "Emi|VOC|Waste", histVars = "Emi|VOC|Waste", vlines = 2020)
```